---
title: "STAT/MATH 495: Problem Set 02"
author: "Kiryu Kawahata"
date: "2017-09-19"
output:
  html_document:
    toc: true
    toc_float: true
    toc_depth: 2
    collapsed: false
    smooth_scroll: false
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, fig.width=8, fig.height=4.5)

# Load packages
library(tidyverse)
library(broom)

# Note the relative file path, and not absolute file path:
# http://www.coffeecup.com/help/articles/absolute-vs-relative-pathslinks/
train <- read_csv("data/train.csv")
```


# Exploratory Data Analysis

```{r}
#Create a test dataframe (if necessary)
test <- train %>% 
  select(-price_doc)

#Housing id as the predictor for price_doc just for overview purposes
Exp_spline <- smooth.spline(x = train$id, y = train$price_doc, df = 3)%>%
  broom::augment()



```


# Model Fit

For this model I chose to test the variable kremlin_km from the training set, which evaluates the distance away from the Kremlin each building is in kilometeres. I chose to test this since it is possible that valuations could be affected by how close a residence is to probably the most influential location in the city/country.

```{r}

#Eliminate extreme values/outliers along the x-axis (distance) past 40 kilometers. I found there to be very few points beyond this distance and decided to use this as a cut off here. 
Outliers <- train %>% 
  filter(kremlin_km <= 40)

#Creation of a spline model using the kremlin_km variable as the predictor, and price_doc as the response using 10 degrees of freedom.
spline_Test <- smooth.spline(x = Outliers$kremlin_km, y = Outliers$price_doc, df = 10)
Spline_Test_Tidy <- spline_Test %>%
  broom::augment()
plot <- ggplot(Spline_Test_Tidy, aes(x=x)) +
  geom_point(aes(y=y)) +
  geom_line(aes(y=.fitted), col= "blue") 
plot

# A prediction based on a sequence of 7662 distance values between 0 and 40 km to generate price estimates. 
new_dist <- seq(from = 0, to = 40, length = 7662)
output <- predict(spline_Test, new_dist) %>% 
  tibble::as.tibble()

#Here I stored a mutated dataset into table "pred_data" which eliminates the x values used in the prediction and created a new column listing corresponding ids formatted for Kaggle submission.

pred_data <- output %>% 
  mutate(id = c(30474:38135)) %>% 
  rename(price_doc = y) %>% 
  select(-x) %>% 
  select(id, price_doc)


submission <- pred_data

```


# Create Submission File

```{r}
#Generates CSV file for submission
write.csv(submission, file = "submission.csv", row.names = FALSE, na = "")
```

